\tool: Programmable, Scalable, Efficient Secure Two-Party Computation

### 2017-10-24 OaklandSubmission/ld.tex
nit
pass over section 3 and 4.

We then present the compilation rules. To prove the correctness
of our compiler, we prove that it preserves the observations. For
security of our compiler, we reduce the security argument to the
security of the cryptographic protocol used to compute the secure
computation circuit.

We present only selected parts of our formalization for space
reasons. Full definitions and proofs can be found in the supplementary
material submitted along with the paper.

@@

The judgment $\rho \vdash e \Downarrow v$ denotes the big-step
evaluation of an expression~$e$ to a value~$v$ under the runtime
environment~$\rho$. Rule ({\sc{E-Var}}) looks up the value of $x$ in
the environment. Rule ({\sc{E-Add}}) inductively evaluates $e_{1}$ and
$e_{2}$, and evaluates to their sum. Rule ({\sc{E-Read}})
evaluates an array read operation. It first evaluates $x$ to an array
value $[\overline{c_{i}}]_{n_{1}}$, and $e$ to a \kw{uint} value
$n$. It then returns $c_{n}$, the $n$-th index value in the array,
provided $n < n_{1}$, the length of the array. Rule ({\sc{E-Inp}})
evaluates to some constant $c$ denoting party $j$'s input. We model
the inputs to be base constants, an array input can be written in the
language as $[\kw{in}_{j}]_{n}$, which can then evaluate using the
rule ({\sc{E-Arr}}). The remaining rules are straightforward, and are
elided for space reasons.

The judgment $\rho \vdash s \Downarrow \rho_{1}; O$ represents the
big-step evaluation of a statement $s$ under environment $\rho$
producing a new environment $\rho_{1}$ and observations $O$. Rule
({\sc{E-Decl}}) evaluates the expression $e$ to $v$, and returns the
updated environment $\rho[x \mapsto v]$, with empty observations. Rule
({\sc{E-If}}) evaluates the guard expression, and then evaluates
either $s_{1}$ or $s_{2}$ accordingly. $\kw{for}$ statements evaluate
through the internal $\kw{while}$ syntax. Specifically, the rule
({\sc{E-For}}) updates $\rho$ with the initial counter value $n_{1}$,
evaluates $\loops{x}{n_{2}}{s}$ to $\rho_{1}; O$, and returns
$\rho_{1} - \{x\}$ (removing $x$ from $\rho_{1}$) and $O$. Rule
({\sc{E-LoopI}}) shows the inductive case for \kw{while}
statements, when $\rho(x) \leq n$. The rule evaluates $s$, producing
$\rho_{1}; O_{1}$. It then restricts $\rho_{1}$ to the domain of
$\rho$ ($[\rho_{1}]_{\mathsf{dom}(\rho)}$) to remove the variables
added by $s$, increments the value if $x$, and evaluates the
\kw{while} statement under this updated environment. Rule
({\sc{E-LoopT}}) is the termination case for \kw{while} statements,
when $\rho(x) > n$. Finally, the rule ({\sc{E-Out}}) evaluates the
expression, and adds its value to the observations.

@@

\subsubsection*{Circuit semantics} The target semantics produces a
circuit to compute over the secret data using an MPC protocol. With
our circuit semantics, we model the \emph{functional} aspect of the
protocol, parametrized by the sharing functions.

During the circuit evaluation, the wire ranges $r$ are
mapped to (random) strings $b$. The semantics of these strings is
given by pairs of encryption-decryption functions, written as
$\mathcal{E}_{m}$ and $\mathcal{D}_{m}$ (where $m$ is either
$\mathcal{A}$ or $\mathcal{B}$). More concretely,
$\mathcal{E}_{m}(c)$ returns a pair of two string $b_{1}$ and $b_{2}$
(shares of the two parties), with the property that
$\mathcal{D}_{m}(b_{1}, b_{2}) = c$. We assume that the underlying MPC
protocol instantiates $\mathcal{E}_{m}$ and $\mathcal{D}_{m}$
appropriately.

@@

     \inferrule*[lab={\footnotesize{T-For}}]
               {
                 \Gamma_{1} = \Gamma, x:\kw{uint}^{\mathcal{P}}\\\\
                 \Gamma_{1} \vdash \loops{x}{n_{2}}{s} \leadsto \loops{x}{n_{2}}{\widetilde{s}} \mid \Gamma_{1}
               }
               {
                 \Gamma \vdash \for{x}{n_{1}}{n_{2}}{s} \leadsto \for{x}{n_{1}}{n_{2}}{\widetilde{s}} \mid \Gamma
               }

@@

  \begin{enumerate}
  \item $\rho \vdash s \Downarrow \rho_{1}; O_{1}$
  \item $\widetilde{\rho} \vdash \widetilde{s} \Downarrow \widetilde{\rho}_{1}; \chi$
  \item $\widehat{\rho}_{1}, \widehat{\rho}_{2} \vdash \chi \Downarrow \widehat{\rho}'_{1}, \widehat{\rho}'_{2}; O_{2}$
  \item $\Gamma_{1} \vdash \rho_{1} \leadsto \widetilde{\rho}_{1}; \widehat{\rho}'_{1}, \widehat{\rho}'_{2}$
  \item $O_{1} = O_{2}$
  \end{enumerate}

@@

\nc{Super high level security theorem}
\subsubsection*{Security theorem} The protocols we generate provide
simulation-based security against a semi-honest adversary, in the
framework of ~\cite{gmw,can00,can01}. At a very high level, in this
framework, parties are modeled as non-uniform interactive turing
machines (ITMs), with inputs provided by an environment $\env$. An
adversary $\adv$, selects and ``corrupts'' one of the parties -
however, $\adv$ still follows the protocol specification. $\adv$
interacts with the $\env$, which observes the view of the corrupted
party. At the end of the interaction, $\env$ outputs a single bit. Two
different interactions are defined: the {\em real world} and an {\em
  ideal world}. In the real interaction, the parties run the protocol
$\prot$ in the presence of $\adv$ and $\env$. Let
$\real_{\prot,\adv,\env}$ denote the binary distribution ensemble
describing $\env$'s output in this interaction. In the ideal
interaction, parties send their inputs to an additional entity, a
trusted functionality machine $\F$ that carries the desired
computation truthfully. Let $\simu$ (the simulator) denote the
adversary in this idealized execution, and $\ideal_{\F,\simu,\env}$
the binary distribution ensemble describing $\env$'s output after
interacting with adversary $\simu$ and ideal functionality $\F$. A
protocol $\prot$ is said to {\em securely realize} a functionality
$\F$ if for every adversary $\adv$ in the real interaction, there is
an adversary $\simu$ in the ideal interaction, such that no
environment $\env$, on any input, can tell the real interaction apart
from the ideal interaction, except with negligible probability (in the
security parameter $\secparam$). More precisely, if the two binary
distribution ensembles above are computationally indistinguishable.
\nc{I'm not happy with the theorem statement.}
\begin{theorem}[Security]\label{theorem:security}
Let $\F$ be a functionality in our source language with outputs (or observations) $O_1$, that is compiled into a protocol $\prot$ in our target language with outputs $O_2$, then $\prot$ securely realizes $\F$.  
\end{theorem}
\nc{We should probably connect things to earlier? Theorem 1 and 2 have very different languages.}
\noindent {\em Proof.} From Theorem \ref{theorem:correctness}, we have
that the observations in $\prot$ and $\F$ are the same (i.e. $O_2 =
O_1$). Now, from the simulation security of our backend (\cite{aby}),
the proof of the above theorem follows. \nc{I dont know how to say
  more.}

\aseem{Can we give a construction of the simulator S in the ideal
  semantics? The simulator S whenever it receives an observable event,
  outputs it to Z, and whenever A receives a string in the real
  semantics, S outputs a random string to Z. Now, with theorem 1,
  observable events are same in the ideal and real semantics, and with
  the security of the crypto backend, the random strings and the
  strings in the protocol are indistinguishable. Is it
  incorrect/naive?

@@

  %% \\
  %% \[
  %% \begin{array}{rrcl}
  %%   \ftext{Value} & v &::=& c \mid [\overline{c_{i}}]_{n}\\
  %%   \ftext{Observation} & O &::=& \cdot \mid c; O\\
  %% \end{array}
  %% \]

>>>>

We then present the compilation rules. To prove the correctness
of our compiler, we prove that it preserves the observations. For
security of our compiler, we reduce the security argument to the
security of the cryptographic protocol used to compute the secure
computation circuit.
\nc{Should we also say that security relies on correctness? (they go together)}
We present only selected parts of our formalization for space
reasons. Full definitions and proofs can be found in the supplementary
material submitted along with the paper.

@@

The judgment $\rho \vdash e \Downarrow v$ denotes the big-step
evaluation of an expression~$e$ to a value~$v$ under the runtime
environment~$\rho$. Rule ({\sc{E-Var}}) looks up the value of $x$ in
the environment. Rule ({\sc{E-Add}}) inductively evaluates $e_{1}$ and
$e_{2}$, and evaluates to their sum. Rule ({\sc{E-Read}})
evaluates an array read operation. It first evaluates $x$ to an array
value $[\overline{c_{i}}]_{n_{1}}$, and $e$ to a \kw{uint} value
$n$. It then returns $c_{n}$, the $n$-th index value in the array,
provided $n < n_{1}$, the length of the array. Rule ({\sc{E-Inp}})
evaluates to some constant $c$ denoting party $j$'s input. We model
the inputs to be base constants, an array input can be written in the
language as $[\kw{in}_{j}]_{n}$, which can then evaluate using the
rule ({\sc{E-Arr}}). The remaining rules are straightforward, and are
elided for space reasons.
\nc{fancy PL folks language :)}
The judgment $\rho \vdash s \Downarrow \rho_{1}; O$ represents the
big-step evaluation of a statement $s$ under environment $\rho$
producing a new environment $\rho_{1}$ and observations $O$. Rule
({\sc{E-Decl}}) evaluates the expression $e$ to $v$, and returns the
updated environment $\rho[x \mapsto v]$, with empty observations. Rule
({\sc{E-If}}) evaluates the guard expression, and then evaluates
either $s_{1}$ or $s_{2}$ accordingly. $\kw{for}$ statements evaluate
through the internal $\kw{while}$ syntax. Specifically, the rule
({\sc{E-For}}) updates $\rho$ with the initial counter value $n_{1}$,
evaluates $\loops{x}{n_{2}}{s}$ to $\rho_{1}; O$, and returns
$\rho_{1} - \{x\}$ (removing $x$ from $\rho_{1}$) and $O$. Rule
({\sc{E-LoopI}}) shows the inductive case for \kw{while}
statements, when $\rho(x) \leq n$. The rule evaluates $s$, producing
$\rho_{1}; O_{1}$. It then restricts $\rho_{1}$ to the domain of
$\rho$ ($[\rho_{1}]_{\mathsf{dom}(\rho)}$) to remove the variables
added by $s$, increments the value if $x$, and evaluates the
\kw{while} statement under this updated environment. Rule
({\sc{E-LoopT}}) is the termination case for \kw{while} statements,
when $\rho(x) > n$. Finally, the rule ({\sc{E-Out}}) evaluates the
expression, and adds its value to the observations.

@@

\subsubsection*{Circuit semantics} The target semantics produces a
circuit to compute over the secret data using an MPC protocol. \nc{We use 2PC and MPC interchangeably. I guess its fine?}With
our circuit semantics, we model the \emph{functional} aspect of the
protocol, parametrized by the sharing functions.

During the circuit evaluation, the wire ranges $r$ are
mapped to (random) strings $b$. The semantics of these strings is
given by pairs of encryption-decryption functions\nc{perhaps call this encode-decode functions since its technically not encryption-decryption? In fact more appropriate might be share-reconstruct, but that would require changing notation so lets not do that.}, written as
$\mathcal{E}_{m}$ and $\mathcal{D}_{m}$ (where $m$ is either
$\mathcal{A}$ or $\mathcal{B}$). More concretely,
$\mathcal{E}_{m}(c)$ returns a pair of two string $b_{1}$ and $b_{2}$
(shares of the two parties), with the property that
$\mathcal{D}_{m}(b_{1}, b_{2}) = c$. We assume that the underlying MPC
protocol instantiates $\mathcal{E}_{m}$ and $\mathcal{D}_{m}$
appropriately.

@@

     \inferrule*[lab={\footnotesize{T-For}}]
               {
                 \Gamma, x:\kw{uint}^{\mathcal{P}} \vdash \loops{x}{n_{2}}{s} \leadsto \loops{x}{n_{2}}{\widetilde{s}} \mid \_
               }
               {
                 \Gamma \vdash \for{x}{n_{1}}{n_{2}}{s} \leadsto \for{x}{n_{1}}{n_{2}}{\widetilde{s}} \mid \Gamma
               }

@@

  \begin{enumerate}[label=(\alph*)]
  \item $\rho \vdash s \Downarrow \rho_{1}; O_{1}$
  \item $\widetilde{\rho} \vdash \widetilde{s} \Downarrow \widetilde{\rho}_{1}; \chi$
  \item $\widehat{\rho}_{1}, \widehat{\rho}_{2} \vdash \chi \Downarrow \widehat{\rho}'_{1}, \widehat{\rho}'_{2}; O_{2}$
  \item $\Gamma_{1} \vdash \rho_{1} \leadsto \widetilde{\rho}_{1}; \widehat{\rho}'_{1}, \widehat{\rho}'_{2}$
  \item $O_{1} = O_{2}$
  \end{enumerate}

@@

\nc{Should we point out that the proof of Theorem 1 is provided elsewhere?}
\subsubsection*{Security theorem} The protocols we generate provide
simulation-based security against a semi-honest adversary, in the
framework of ~\cite{gmw,can00,can01}. At a very high level, in this
framework, parties are modeled as non-uniform interactive turing
machines (ITMs), with inputs provided by an environment $\env$. An
adversary $\adv$, selects and ``corrupts'' one of the parties -
however, $\adv$ still follows the protocol specification. $\adv$
interacts with the $\env$, which observes the view of the corrupted
party. At the end of the interaction, $\env$ outputs a single bit. Two
different interactions are defined: the {\em real world} and an {\em
  ideal world}. In the real interaction, the parties run the protocol
$\prot$ in the presence of $\adv$ and $\env$. Let
$\real_{\prot,\adv,\env}$ denote the binary distribution ensemble
describing $\env$'s output in this interaction. In the ideal
interaction, parties send their inputs to an additional entity, a
trusted functionality machine $\F$ that carries the desired
computation truthfully. Let $\simu$ (the simulator) denote the
adversary in this idealized execution, and $\ideal_{\F,\simu,\env}$
the binary distribution ensemble describing $\env$'s output after
interacting with adversary $\simu$ and ideal functionality $\F$. A
protocol $\prot$ is said to {\em securely realize} a functionality
$\F$ if for every adversary $\adv$ in the real interaction, there is
an adversary $\simu$ in the ideal interaction, such that no
environment $\env$, on any input, can tell the real interaction apart
from the ideal interaction, except with negligible probability (in the
security parameter $\secparam$). More precisely, if the two binary
distribution ensembles above are computationally indistinguishable.

We shall assume a cryptographic MPC backend that securely implements any circuit $\chi$ that is output by our compiler. In more detail, this means that for every source program $s$, let $\chi$ be the circuit output by our compiler (as in Theorem \ref{theorem:correctness}). We assume that there exists a two-party secure computation protocol $\prot$ that securely realizes the functionality $\chi$ and we will call the corresponding simulator for the protocol as $\simu_{\tiny{2pc}}$ (that runs on input $\chi$ and the output produced by $\chi$ on the parties inputs). We note that the work of \cite{aby} provides such a protocol $\prot$ and simulator $\simu_{\tiny{2pc}}$ for all circuits $\chi$ output by our compiler. We are now ready to state and prove our security theorem.

\begin{theorem}[Security]\label{theorem:security}
Let $s$ be any functionality or program in our source language with outputs (or observations) $O_1$, that is compiled into a circuit $\chi$ (as defined in Theorem \ref{theorem:correctness}). Let protocol $\prot$ be the two-party secure computation protocol that securely realizes $\chi$ (as defined above). Then, $\prot$ securely realizes $s$.  
\end{theorem}

\noindent {\em Proof.} Our simulator $\simu$ simply runs our compiler on program $s$ to obtain $\chi$ and upon receiving output $O_1$, executes $\simu_{\tiny{2pc}}$ on $\chi$ and $O_1$. Let $O_2$ be the outputs (or observations) of $\chi$. First, from Theorem \ref{theorem:correctness}, we have that the observations in $s$ and $\chi$ are the same (i.e. $O_2 = O_1$). Now, from the security of $\prot$, we have that the simulated view output by $\simu_{\tiny{2pc}}$ (with circuit $\chi$ and output $O_2$) is indistinguishable from the real view of the $\prot$ (when executed on circuit $\chi$ and when the output is $O_2$). Combining these two statements, the proof of the theorem follows. 
\aseem{Can we give a construction of the simulator S in the ideal
  semantics? The simulator S whenever it receives an observable event,
  outputs it to Z, and whenever A receives a string in the real
  semantics, S outputs a random string to Z. Now, with theorem 1,
  observable events are same in the ideal and real semantics, and with
  the security of the crypto backend, the random strings and the
  strings in the protocol are indistinguishable. Is it
  incorrect/naive?

@@

\nc{OK now?}
  %% \\
  %% \[
  %% \begin{array}{rrcl}
  %%   \ftext{Value} & v &::=& c \mid [\overline{c_{i}}]_{n}\\
  %%   \ftext{Observation} & O &::=& \cdot \mid c; O\\
  %% \end{array}
  %% \]
